class: bg-main1 split-30 hide-slide-number

.column.bg-main3[
]
.column.slide-in-right[
.sliderbox.bg-main2.vmiddle[
.font3[`import package`]
]]

---

class: middle center bg-main1 hide-slide-number

# Importing packages as R variables

--
  ## One of the ways to import Python packages to be used in an R Script, is to import them as R environment variables, given that {reticulate} is already configured:
  
--

```{r eval=FALSE, echo=TRUE}
np <- reticulate::import("numpy")
np$array() # equivalente ao np.array
```
  
---

class: middle center bg-main1 hide-slide-number

# Checking the package availability from R

--
  ## Even though it is easy to import packages, sometimes we do not have any ways to check if a specific package is installed in the enviroment that was set up for {reticulate}... So, in order to ensure that this package is installed and available to be imported, or to trigger an installation of a specific package from R scripts, these commands can be used:
  
--

```{r eval=FALSE, echo=TRUE}
reticulate::py_module_available('fastAPI')
reticulate::py_install("fastAPI")
```
  
---

class: middle center bg-main1 hide-slide-number

# Importing functions/scripts in Python

--
  ## To avoid repeating code that was already developed in Python, it is possible to `source` them to be used in R:
  
--

```{r eval=FALSE, echo=TRUE}
reticulate::source_python("functions/teste.py")
```
  
---

class: middle center bg-main1 hide-slide-number

# Python console inside RStudio

--
  ## There are plenty of ways to use R alongside Python in a more direct way, nonetheless, sometimes it is necessary to open a Python console inside RStudio, and the way to do it is by running the command below:
  
--

```{r eval=FALSE, echo=TRUE}
reticulate::repl_python()
```
  
---